\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{hyperref}
\textheight=10in
\pagestyle{empty}
\raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex}

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\area} [2] {
	\vspace*{-9pt}
	\begin{verse}
		\textbf{#1}   #2
	\end{verse}
}
\newcommand{\lineunder} {
	\vspace*{-8pt} \\
	\hspace*{-18pt} \hrulefill \\
}
\newcommand{\header} [1] {
	{\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
	\vspace*{-6pt} \lineunder
}
\newcommand{\subheader} [1] {
	{\hspace*{-9pt}\vspace*{6pt} \textsc{#1}}
	\vspace*{-6pt}
}
\newcommand{\employer} [3] {
	{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}
\newcommand{\contact} [3] {
	\vspace*{-10pt}
	\begin{center}
		{\Huge \scshape {#1}}\\
		#2 \\ #3
	\end{center}
	\vspace*{-8pt}
}


\begin{document}
\vspace*{-40pt}
\vspace*{-10pt}
\begin{center}
{\Huge \scshape {Christian A. Stratton}} \\
\faMapMarker \ 102 Branegan Court, Apt A. Bozeman, MT, 59715 \\
\faEnvelope \ \href{mailto:christianstratton@montana.edu}{christianstratton@montana.edu} \\ 
\faGlobe \ \href{https://strattonch.github.io/christianstratton/}{https://strattonch.github.io/christianstratton/} \\
\faPhone \ (406) 261-9426 \\ 
\end{center}
\vspace*{2mm}

\header{Summary}
\vspace*{2mm}

Post-doctoral researcher in statistics with consulting, research, and
teaching experience. Strong analytical skills pertaining to spatial
statistics, Bayesian computation, and analysis of ecological data types.
Research interests include: Bayesian computation, spatial statistics,
species distribution modeling, modeling of wildlife disease, data
visualization, and teaching techniques for data science.

\header{Education}
\vspace*{2mm}

\textbf{Montana State University} \hfill Bozeman, MT

Bachelor of Science with Honors in Mathematics (focus: Statistics)
\hfill December 2016

\vspace{2mm}

\textbf{Montana State University} \hfill Bozeman, MT

Master of Science in Statistics \hfill May 2018

\vspace{2mm}

\textbf{Montana State University}\hfill Bozeman, MT

Doctor of Philosophy in Statistics \hfill May 2022

Dissertation:
\textit{Bayesian Hierarchical Latent Variable Models for Ecological Data Types}

Advisors: Dr.~Andrew Hoegh and Dr.~Jennifer Green

\vspace{2mm}

\header{Peer-reviewed Journal Articles}
\vspace*{2mm}

\subheader{In Review}
\vspace*{2mm}

\textbf{Stratton, C.}, A. Hoegh, T.J. Rodhouse, J.L. Green, K.M. Banner,
and K.M. Irvine. ``Clustering and unconstrained ordination with
Dirichlet process mixture models.'' In review in
\textit{Methods in Ecology and Evolution}. \vspace*{2mm}

\textbf{Stratton, C.}, K.M Irvine, K.M. Banner, E.S. Almberg, D. Bachen,
and K. Smucker. ``Joint spatial modeling bridges the gap between
disparate disease surveillance and population monitoring efforts
informing conservation of at-risk bat species.'' In review in the
\textit{Journal of Agricultural, Biological, and Environmental Statistics}.
\vspace*{2mm}

Oram, J., K.M. Banner, \textbf{C. Stratton}, and K.M. Irvine.
``Verifying species classification labels using stratified-by-species
sampling reduces cost of long-term acoustic monitoring.'' In review in
\textit{Methods in Ecology and Evolution}. \vspace*{2mm}

Retel, C., A.J. Strien, K.M. Irvine, and \textbf{C. Stratton}. ``Trends
in plant cover derived from vegetation-plot data using ordinal
zero-augmented beta regression.'' In review in the
\textit{Journal of Vegetation Science}. \vspace*{2mm}

\subheader{Accepted}
\vspace*{2mm}

\textbf{Stratton, C.}, K.M. Irvine, K.M. Banner, W.J. Wright, C. Lausen,
J. Rae. 2022. \href{https://doi.org/10.1111/2041-210X.13831}{``Coupling
validation effort with \emph{in situ} bioacoustic data improves
estimating relative activity and occupancy for multiple species with
cross-species misclassifications.''}
\textit{Methods in Ecology and Evolution}, 13(6), p.~1288 -- 1303.
\vspace*{2mm}

\textbf{Stratton, C.}, J.L. Green, and A. Hoegh. 2021.
\href{https://doi.org/10.5070/T513146468}{``Not just normal: Exploring
power with Shiny apps.''}
\textit{Technology Innovations in Statistics Education}, 13(1), p.~1 --
37. \vspace*{2mm}

\textbf{Stratton, C.}, A.J. Sepulveda, and A. Hoegh. 2020.
\href{https://doi.org/10.1111/2041-210X.13442}{``\texttt{msocc:} Fit and
analyze computationally efficient multi-scale occupancy models in
\texttt{R}.''} \textit{Methods in Ecology and Evolution}, 11(9), p.~1113
-- 1120. \vspace*{2mm}

Hoegh, A., K. Flagg, and \textbf{C. Stratton}. 2018. Contributed comment
on Article by Bradley, Holan, and Wikle
\href{https://eds.p.ebscohost.com/abstract?site=eds\&scope=site\&jrnl=19360975\&AN=138950462\&h=fupOc1pyeH8dv67mdPoRzhYvo96LS\%2bzCYNHIjAcMPojnVBydkua\%2fXFU6RanU78MDh8WNMlzPVI\%2fBxvaUiWvg\%2bw\%3d\%3d\&crl=c\&resultLocal=ErrCrlNoResults\&resultNs=Ehost\&crlhashurl=login.aspx\%3fdirect\%3dtrue\%26profile\%3dehost\%26scope\%3dsite\%26authtype\%3dcrawler\%26jrnl\%3d19360975\%26AN\%3d138950462}{Invited
commentary on ``Computationally efficient multivariate spatio-temporal
models for high-dimensional count-valued data'' by Jonathan R. Bradley,
Scott H. Holan, and Christopher K. Wikle.}
\textit{Bayesian Data Analysis}, 13(1), p.~253 -- 310. \vspace*{2mm}

Irvine, K.M., K.M. Banner, \textbf{C. Stratton}, W.M. Ford, and B.E.
Reichert. 2022. \href{https://doi.org/10.1002/ecs2.4142}{``Statistical
assessment on determining local presence of rare bat species.''}
\textit{Ecosphere}, 13(6), p.~e4142. \vspace*{2mm}

Khalighifar, A., B.S. Gotthold, E. Adams, J. Barnett, L.O. Beard, E.R.
Britzke, P.A. Burger, K. Chase, Z. Cordes, P.M. Cryan, E. Ferrall, C.T.
Fill, S.E. Gibson, G.S. Haulton, K.M. Irvine, L.S. Katz, W.L. Kendall,
C.A. Long, O.M. Aodha, T. McBurney, S. McCarthy, M.W. McKown, J.
O'Keefe, L.D. Patterson, K.A. Pitcher, M. Rustand, J.L. Segers, K.
Seppanen, J.L. Simers, \textbf{C. Stratton}, B.R. Straw, T.J. Weller,
and B.E. Reichert. 2022.
\href{https://doi.org/10.1111/1365-2664.14280}{``\emph{NABat ML}:
Utilizing deep learning to enable crowdsourced development of automated,
scalable solutions for documenting North American bat populations.''}
\textit{Journal of Applied Ecology}, 56(11), p.~2849 -- 2862.
\vspace*{2mm}

Sepulveda, A.J., A. Hoegh, J.A. Gage, S.L Caldwell-Eldridge, J.M. Birch,
\textbf{C. Stratton}, P.R. Hutchins, E.P. Barnhart. 2021.
\href{https://doi.org/10.3389/fevo.2021.620715}{``Integrating
environmental DNA results with diverse data sets to improve
biosurveillance of river health.''}
\textit{Frontiers in Ecology and Evolution}, 9, p.~1 -- 13.
\vspace*{2mm}

Sepulveda, A. J., C. Schmidt, J. Amberg, P. Hutchins,
\textbf{C. Stratton}, C. Mebane, M. B. Laramie, and D. S. Pilliod. 2019.
\href{https://doi.org/10.1002/ecs2.2843}{``Adding invasive species
biosurveillance to the U.S. Geological Survey streamgage network.''}
\textit{Ecosphere}, 10(8), p.~1 -- 17. \vspace*{2mm}

\header{Peer-reviewed Technical Reports}
\vspace*{2mm}

\textbf{Stratton, C.}, B.R. Straw, J.H. Cox, K.M. Irvine, F.C. Tousley,
and B.E. Reichert. 2023.
\href{https://doi.org/10.5066/P9H8NEOY}{``Attributed North American
Grid-Based Offshore Sampling Frames: U.S. Geological Survey data
release.''} \vspace*{2mm}

\textbf{Stratton, C.}, K.M. Irvine. 2022. Summertime analysis
statistical report for Little Brown, Northern Long-eared, and Tricolored
bat species status assessment. Chapter B in Straw, B.R, J. A. Martin,
J.D Reichard, and B.E Reichert, editors.
\href{https://doi.org/10.7944/P9B4RWEU}{``Analytical assessments in
support of the U.S. Fish and Wildlife Service 3-Bat species status
assessment. Cooperator report prepared in cooperation with the U.S.
Geological Survey, United States Fish and Wildlife Service and Bat
Conservation International.''} \vspace*{2mm}

\textbf{Stratton, C.}, A. Hoegh, K. M. Irvine, K. Legg, K. McCloskey, E.
Shanahan, M. Tercek, and D. Thoma. 2019.
\href{https://irma.nps.gov/DataStore/DownloadFile/631136}{``Assessing
spatial and temporal patterns in sagebrush steppe vegetation
communities, 2012-2018: Grand Teton National Park.''} Natural Resource
Report NPS/GRYN/NRR-2019/2020. National Park Service, Fort Collins,
Colorado. \vspace*{2mm}

Irvine, K.M., and \textbf{C. Stratton}. 2021.
\href{https://doi.org/10.5066/P9XZ8D6N.}{``Rangewide summertime model
predictions for three bat species (\textit{Myotis lucifigus},
\textit{Myotis septentrionalis}, and \textit{Perimyotis subflavus}) from
acoustic and mist net data 2010 to 2019: US Geological Survey data
release.''} \vspace*{2mm}

Udell, B.J., B.R. Straw, T.L. Cheng, K. Enns, W.F. Frick, B. Gotthold,
K.M. Irvine, C. Lausen, S. Loeb, J.D. Reichard, T.J. Rodhouse, D. Smith,
\textbf{C. Stratton}, W.E. Thogmartin, and B.E. Reichert. 2022.
\href{https://doi.org/10.5066/P92JGACB}{``Status and trends of North
American bats: Summer occupancy analysis 2010-2019.''} U.S. Fish and
Wildlife Service. \vspace*{2mm}

Wessel, S.A., L. Jones, E. Kramer, \textbf{C. Stratton}, L. Shoemaker,
and D. Laughlin. 2020.
\href{https://journals.uwyo.edu/index.php/uwnpsrc/article/view/6791/6301}{``Predictability
and stability of sagebrush-steppe restoration in a changing climate.''}
National Park Service Annual Report Vol. 43. \vspace*{2mm}

\header{Presentations}
\vspace*{2mm}

\textbf{Stratton, C.}, K.M. Irvine, K.M. Banner, E. Almberg, D. Bachen,
and K. Smucker. ``Joint spatial modeling of ecological response and
disease processes improves estimator precision.'' 2023. Talk given at
the Joint Statistical Meetings. Toronto, Ontario, Canada. \vspace*{2mm}

\textbf{Stratton, C.}, K.M. Irvine, K.M. Banner, E. Almberg, D. Bachen,
and K. Smucker. ``A statistical framework for integrating White-nose
syndrome surveillance data and acoustic population monitoring
data.''2023. Talk given to the U.S. Geological Survey Disease
Coordination Group. Virtual. \vspace*{2mm}

\textbf{Stratton, C.}, K.M. Irvine, K.M. Banner, E. Almberg, D. Bachen,
and K. Smucker. ``Leveraging WNS surveillance and NABat data improves
estimation of disease spread and bat activity.'' 2023. Poster presented
at the Whitenose Syndrome National Meeting. Palm Springs, California,
USA. \vspace*{2mm}

\textbf{Stratton, C.}, K.M. Irvine, E. Almberg, K. Smucker, and J. Gude.
``Joint spatial modeling of relative activity and disease processes.''
2022. Poster presented at the ENVR 2022 Workshop: Environmental and
Ecological Statistical Research and Applications with Societal Impacts.
Provo, Utah, USA. \vspace*{2mm}

\textbf{Stratton, C.}, K.M. Irvine, E. Almberg, K. Smucker, and J. Gude.
``Bats \& Stats: Assessing Impacts of White-nose Syndrome on Western Bat
Species.'' 2022. Talk given at the Northern Rocky Mountain Science
Center. Bozeman, Montana, USA. \vspace*{2mm}

\textbf{Stratton, C.}, A. Hoegh, K.M. Irvine, K.M. Banner. 2021.
``Clustering and ordination with Dirichlet process mixture models.''
Invited talk given at the Joint Statistical Meetings. Virtual.
\vspace*{2mm} \newpage \textbf{Stratton, C.}, J.L. Green. 2021. ``Beyond
normal: Understanding power through \texttt{R} Shiny.'' Poster presented
at the United States Conference on Teaching Statistics. Virtual.
\vspace*{2mm}

\textbf{Stratton, C.}, A. Hoegh, and J.L. Green. 2018. ``Predicting
pitch type: A case study in Bayesian hierarchical multinomial
regression.'' Invited talk given at the Joint Statistical Meetings.
Vancouver, Canada. \vspace*{2mm}

\textbf{Stratton, C.}, A. Hoegh, and J.L. Green. 2018. ``Unraveling
Kershaw's dominance.'' Poster presented at The Cascadia Symposium on
Statistics in Sports. Vancouver, Canada. \vspace*{2mm}

\textbf{Stratton, C.} and J.L. Green. 2018. ``The power of technology: A
Shiny applet assisted approach to teaching statistical power.'' Poster
presented at the Electronic Conference on Teaching Statistics. Virtual.
\vspace*{2mm}

\header{Peer-reviewed Science Software}
\vspace*{2mm}

\textbf{Stratton, C.}, A. Hoegh, A. Sepulveda, and K.M. Banner. 2020.
``\texttt{msocc}.'' \texttt{R} package to support computationally
efficient implementation of Bayesian multi-scale occupancy models.
\vspace*{2mm}

\header{Experience}
\vspace*{2mm}

\textbf{Montana State University} \hfill Bozeman, MT

\textit{Post-doctoral researcher} \hfill July 2022 \textbar{} Present

Advisors: Dr.~Kathryn Irvine (USGS) and Dr.~Katharine Banner (MSU)

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Developed statistical modeling frameworks for ecological data structures
    \item Authored multiple peer-reviewed journal articles and technical reports
    \item Communicated complicated statistical models to domain experts from multiple agencies
    \item Co-mentored a graduate-level statistician in support of research and analyses
\end{itemize}

\textbf{U.S. Geological Survey} \hfill Bozeman, MT

\textit{Student contractor} \hfill August 2020 \textbar{} July 2022

Supervisor: Dr.~Kathryn Irvine (USGS)

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
   \item Provided analyses for Endangered Species Act listing decisions
   \item Authored peer-review journal articles and technical reports
   \item Collaborated with scientists from multiple domains 
\end{itemize}

\textbf{Montana State University} \hfill Bozeman, MT

\textit{Math Learning Center Supervisor} \hfill June 2019 \textbar{}
December 2019

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
   \item Supervised graduate and undergraduate tutors
   \item Coordinated monthly meetings
   \item Proposed and implemented logistical improvements including novel tutoring practices
   \item Coached new tutors on how to effectively communicate mathematics
\end{itemize}

\textbf{Montana State University} \hfill Bozeman, MT

\textit{Graduate Research Assistant} \hfill January 2019 \textbar{}
August 2020

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
   \item Resolved a wide scope of ecological problems using various techniques
   \item Collaborated and communicated with domain experts in ecology and land-resource management
   \item Developed models and tools to aid collaborators
   \item Authored papers, web applications, and R packages
\end{itemize}

\textbf{Montana State University} \hfill Bozeman, MT

\textit{Statistical Consultant} \hfill August 2017 \textbar{} May 2018

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
   \item Communicated with clients
   \item Identified solutions to a wide scope of problems
   \item Successfully collaborated across departments to resolve problems
\end{itemize}

\textbf{Montana State University} \hfill Bozeman, MT

\textit{Graduate Teaching Assistant} \hfill January 2017 \textbar{}
December 2018

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
   \item Implemented active learning teaching strategies for introductory statistics
   \item Planned and prepared course materials 
   \item Coached students in a collaborative learning environment
\end{itemize}

\textbf{Montana State University} \hfill Bozeman, MT

\textit{Math Learning Center Tutor} \hfill August 2014 \textbar{}
December 2016

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Tutored students in a wide array of mathematics and statistics
    \item Implemented active learning tutoring strategies
    \item Facilitated management of operations in tutoring center
\end{itemize}

\header{Teaching Experience}
\vspace*{2mm}

\textbf{Guest Lecturer} \hfill Bozeman, MT

\emph{STAT 408: Statistical Computing and Graphics Analysis} \hfill S22

Provided guest lectures on data visualization with the
\texttt{tidyverse} and implementing version control software in
statistical analyses to undergraduate-level statistics students.
\vspace*{2mm}

\textbf{Guest Lecturer} \hfill Bozeman, MT

\emph{STAT 402/502: Intermediate Mathematical Statistics} \hfill S19

Provided guest lecture on interpreting statistical power to
undergraduate-level and graduate-level mathematical statistics students
using \texttt{R\ Shiny}. \vspace*{2mm}

\textbf{Teaching Assistant} \hfill Bozeman, MT

\emph{STAT 411/511: Methods for Data Analysis I} \hfill S19

Teaching assistant responsibilities included: grading homeworks and
exams, writing and leading interactive lab assignments, and providing
intermittent lectures on coding in \texttt{R} with an emphasis on data
visualization. \vspace*{2mm}

\textbf{Instructor of Record} \hfill Bozeman, MT

\emph{STAT 217: Intermediate Statistical Concepts} \hfill F18

Lead instructor responsibilities included: leading lectures, writing
lecture notes, writing and grading homeworks and exams, writing lab
assignments, and supervising teaching assistants. \vspace*{2mm}

\textbf{Instructor of Record} \hfill Bozeman, MT

\emph{STAT 216: Introduction to Statistics} \hfill S17, F17, S18

Lead instructor responsibilities included: leading lectures, writing
lecture notes, writing and grading homeworks and exams, and writing lab
assignments. \vspace*{2mm}

\textbf{Teaching assisstant} \hfill Bozeman, MT

\emph{STAT 216: Introduction to Statistics} \hfill F15, S16, F16

Teaching responsibilities included: facilitating discussion during
in-class activities and holding office hours for students. \vspace*{2mm}

\header{Service}

\textbf{Montana Chapter of the American Statistical Association}
\hfill Bozeman, MT

\emph{Chapter Secretary and Council of Chapters Representative}
\hfill Sept 2022 \textbar{} Present

Responsibilities included facilitating coordination of annual meetings,
keeping meeting notes, and attending the Council of Chapters session at
the Joint Statistical Meetings. \vspace*{2mm}

\textbf{Bozeman Environmental and Ecological Statistics (BEES)}
\hfill Bozeman, MT

\emph{Co-President} \hfill Sept 2022 \textbar{} Present

The BEES research group is a group focused on mentoring graduate
students with interest in statistical research motivated by
environmental and ecological applications. Responsibilities as
co-president include coordinating bi-weekly meetings, mentoring graduate
students, providing papers for literature review sessions, maintaining
the group website, and coordinating invited speaker presentations.
\vspace*{2mm}

\textbf{Annals of Applied Statistics}

\emph{Referee} \hfill 2023 \textbar{} Present

Refereed papers for the \emph{Annals of Applied Statistics} journal.
\vspace*{2mm}

\textbf{Montana State University STEAM Day} \hfill Bozeman, MT

\emph{Workshop Presenter} \hfill April 2023

MSU STEAM Day is a one-day conference that includes hands-on workshops
in the STEAM fields of science, technology, engineering, art and math
for girls in grades six, seven, and eight. Responsibilities included
presenting an interactive activity introducing statistical inference
using the dice game Pass the Pigs. \vspace*{2mm}

\textbf{DataFest} \hfill Bozeman, MT

\emph{Volunteer judge} \hfill 2019, 2022

Volunteer responsibilities included providing guidance to
undergraduate-level and graduate-level students competing in DataFest
competition. \vspace*{2mm}

\header{Skills}
\vspace*{2mm}
\begin{tabular}{ l l }
  Statistical computing languages:  & R, Julia, SAS \\
    Other programming languages:         &  HTML, Markdown, Quarto, R Shiny, Tableau \\
  Probabilistic programming languages:         & BUGS, JAGS, NIMBLE, Stan \\
    Database management systems:         & SQL, SQLite, Microsoft Excel \\
    Word processors:       & LaTeX, Microsoft Word \\
    Operating systems:       & Windows, Mac OS \\
\end{tabular}
\vspace*{2mm}

\header{Awards}
\vspace*{2mm}

\textbf{Three Minute Thesis Competition Finalist} \hfill Bozeman, MT

Finalist for the Three Minute Thesis competition \hfill February 2020

\vspace*{2mm}

\textbf{Dr. William A. Stannard Award for Excellence} \hfill Bozeman, MT

Recognition of outstanding graduate student teaching \hfill May 2018

\vspace*{2mm}

\textbf{Outstanding Graduate Student Award} \hfill Bozeman, MT

Recognition of superior academic achievement among graduate students
\hfill May 2017

\vspace*{2mm}

\textbf{John L. Magaret Math/Science Scholarship} \hfill Bozeman, MT

Recipient of scholarship for outstanding academic achievement
\hfill January 2017

\vspace*{2mm}

\textbf{Milton-Chauner Math Scholarship} \hfill Bozeman, MT

Recipient of scholarship for outstanding academic achievement
\hfill August 2016

\vspace*{2mm}

\textbf{Outstanding Undergraduate Student Award} \hfill Bozeman, MT

Recognition of superior academic achievement among undergraduate
students \hfill May 2016

\vspace*{2mm}

\textbf{Outstanding Scholar Award} \hfill Bozeman, MT

Recognition of superior academic performance \hfill May 2016

\vspace*{2mm}

\textbf{Montana State University System Award} \hfill Bozeman, MT

Scholarship for outstanding academic performance \hfill December 2015

\vspace*{2mm}

\textbf{Phi Kappa Phi} \hfill Bozeman, MT

Member of Phi Kappa Phi, a national multi-disciplinary honor society
\hfill March 2015

\vspace*{2mm}

\textbf{Pi Mu Epsilon} \hfill Bozeman, MT

Member of Pi Mu Epsilon, a national mathematics honor society
\hfill December 2014

\vspace*{2mm}

\header{References}
\vspace*{2mm}

\textbf{Dr.~Jennifer Green} \hfill East Lansing, MI

\emph{Michigan State University}

Associate professor of statistics
\hfill \href{mailto:jg@msu.edu}{jg@msu.edu}

\vspace*{2mm}

\textbf{Dr.~Andrew Hoegh} \hfill Bozeman, MT

\emph{Montana State University}

Assistant professor of statistics
\hfill \href{mailto:andrew.hoegh@montana.edu}{andrew.hoegh@montana.edu}

\vspace*{2mm}

\textbf{Dr.~Kathryn Irvine} \hfill Bozeman, MT

\emph{U.S. Geological Survey}

Research statistician
\hfill \href{mailto:kirvine@usgs.gov}{kirvine@usgs.gov}

\vspace*{2mm}
\end{document}
